Metal Mixing and Ejection in Dwarf Galaxies is Dependent on Nucleosynthetic Source

### 2018-07-31 main.tex

One-zone chemical evolution models assume homoegeneous mixing of metals from recent star formation into gas available for future star formation \citep[e.g.][]{Lanfranchi2006b,Kirby2011-III,Cote2017,Andrews2017}. While this assumes that metal mixing in the ISM plays no role in delaying future enrichment in star formation, accounting for this process is challening. More complex models \citep[e.g.][]{SchonrichBinney2009,Pezzulli2016} employ multiple (usually radial) zones or follow multiple gas phases to attempt to account for these effects. How to properly account for multi-phase mixing, however, is still poorly understood. This is in large part because both these models and large-scale cosmological simulations lack the necessary fidelity to capture the detailed, multi-phase mixing process of metals in the ISM directly. 
%Consequently, following metal mixing, if treated in these models, requires assumptions about how metals mix within the ISM and how metals couple to galactic outflows. 
Recent hydrodynamics simulations have employed parameteric models to account for unresolved sub-grid metal mixing \citep{PanScannapiecoScalo2013,Sarmento2017}, which plays an important role in determining the chemical properties of galaxies \citep[e.g.][]{Shen2010, Pilkington2012, Few2012, Brook2014, FengKrumholz2014, Escala2018, Armillotta2018} and the enrichment process and chemical signatures of the first stars \citep[e.g.][]{Jeon2015,Ritter2015,Smith2015}. Detailed hydrodynamics simulations incorporating a realistic multi-phase ISM and detailed stellar feedback are required to understand the details of metal mixing and metal outflows in galaxies.

@@

It is becoming increasingly valuable to develop a concrete theoretical understanding of galactic chemical evolution as a result of multiple, recent observational campaigns to probe detailed stellar abundances in our Milky Way and the Local Group, such as SEGUE \citep{Yanny2009}, RAVE \citep{Kunder2017}, APOGEE \citep{Anders2014}, and GALAH \citep{Buder2018}. Stellar abundances are directly imprinted with the enrichment pattern of their star forming cloud, whose chemical properties are determined by the process of turbulent metal mixing in the ISM. The degree to which we can associate "chemically tagged" stars as co-eval depends directly upon our understanding of metal enrichment and metal mixing in the ISM. Furthermore, this understanding is critical for using these observations to further deduce properties of a galaxy's evolutionary history. \textbf{One key aspect of this work has been a significant effort to characterize the number of independent dimensions accessible by the multi-dimensional chemical abundances observed in these studies \citep[e.g][]{Ting2012, Hogg2016,Jofre2017,Price-Jones2018}. Thus far, these studies have remained uninformed by hydrodynamics simulations and, conversely, these results cannot yet be used to constrain simulations. Doing so requires the kinds of high resolution, galaxy-scale multi-element chemodynamical simulations that have only become feasible recently.}

@@

@@

We find two major results. First, nearly all of the metals reside within neutral gas, mostly in the CNM; only a few percent reside in the hot phases. The exact fraction varies with each species, most notably for carbon; these fluctuations are at most $\sim 10$\%. This is not surprising, as the cold phases represent the majority of the mass in the ISM, but, as shown in Section~\ref{sec:statistics}, even though the cold phases harbor most of the metals, the hot phases have significantly higher metal mass fractions. Second, only a small fraction of produced metals are retained within the dwarf galaxy, in agreement with observations of nearby dwarf galaxies \citep[see][]{Kirby2011-metals, McQuinn2015}; however, the retention factor varies. The top panel shows a qualitative disagreement between the retention fractions of N and Ba (about 20\% for each) as compared to the rest of the metals ($\sim$ 4 -- 5\%). This suggests that individual metals \textit{do not} share the same dynamical evolution. Clearly, metal enrichment in galaxies is a phenomenon that cannot be fully captured using single, global metallicity field. In this particular case, assuming that all metals behave the same would underestimate the N and Ba enrichment by a factor of up to five, at least for low mass dwarf galaxies.

@@

%mm should most of this material be in the introduction, and just the last two sentences be here?
%   AE: I agree this is mostly redundant. I removed this
%Chemical evolution models make varying approximations as to what fraction and on what timescales newly formed metals populate a galaxy's ISM and become available to enrich future generations of stars. In the simplest models, new metals are instantaneously available upon the formation of new stars, ignoring delays due to stellar lifetimes (\textit{refs, but maybe not if included in introduction}). Accounting for delays due to individual stellar lifetimes, loss from galactic winds, and dilution from accretion of pristine gas leads to models that can more accurately capture a variety of mean chemical properties of galaxies with some ability to account for spreads in abundances. 
In hydrodynamics simulations, there has been substantial work understanding how metals, often characterized as passive scalar fields, diffuse in both turbulent boxes and global galaxy models. However, there is not  yet a complete model for how metals should mix and evolve in the complex, multi-phase ISM of real galaxies. To build towards this, we characterize the metal evolution and distributions in our galaxy below.

@@

The log-normal distribution is found often in nature, generally describing processes with non-negative values that grow with time. In astrophysics, for example, the log-normal distribution can be used to describe the time evolution of the star formation rate density \citep[see ][]{Gladders2013,Abramson2016,Diemer2017}. In addition, as expected from analytic theory \citep{Vazquez-Semadeni1994}, isothermal turbulence gives rise to log-normal density probability distribution functions \citep[PDFs;][]{Padoan1997, Passot1998, Ostriker1999,PadoanNordlund2002,KrumholzMcKee2005,Federrath2008}. Although these PDFs are only log-normal in simulations containing a more realistic, multi-phase ISM \citep{Scalo1998} if the disk is very stable \citep{WadaNorman2007}, individual phases within the ISM do exhibit some log-normality \citep{Tasker2009, Tasker2011,Joung2009,PriceFederrathBrunt2011, HopkinsQuataertMurray2012}. It has been shown that the 3D density PDF and the column density PDF, in both simulations and observations, have a characteristic shape. This includes a log-normal component, generated by multiplicative processes (shocks and the turbulent cascade in the ISM) and a power-law component at high densities arising from the additive combination of individual, self-gravitating cloud structures \citep{Vazquez-Semadeni1994,Burkhart2009, FederrathKlessen2013, Collins2012, Myers2015, Burkhart2017, Chen2017}.

@@

We follow \cite{Collins2012}, \citet{Burkhart2017}, and \citet{Chen2017} in constructing our piecewise PDF. We define the distribution of metals in the ISM as a function of the fraction of mass contained at a given metallicity, $Z$, or metal mass fraction, $Z_i$, where $i$ denotes an individual element. This PDF is given as
\begin{align*}
  p(Z) =
  \begin{cases}
    \frac{N}{\sigma Z \sqrt{2\pi}} \rm{exp}\left[-\frac{(\rm{ln}(Z) - \mu)^2}{2\sigma^2}\right],
    & Z < Z_{\rm{t}} \\
    % \multicolumn{1}{@{}c@{\quad}}{1} % variant with \multicolumn
    N p_o Z^{-\alpha},
    & Z > Z_{\rm{t}}
\end{cases}
\end{align*}
where $N$ is a normalization constant, $p_o$ ensures continuity between the two components, $\mu$ and $\sigma$ are the log-mean and width of the log-normal component, $\alpha$ is the power-law slope,  and Z$_{\rm t}$ is the metal fraction at the transition between the log-normal and power-law components. When fitting this PDF, we only enforce continuity and $\int_0^{\infty} p(Z) dZ = 1$, leaving $\alpha$, $\mu$, $\sigma$, and $Z_{\rm t}$ as free parameters. These conditions set $N$ and $p_o$ to
\begin{equation}
N = \frac{1}{2} \left[ 1 + \rm{erf}\left( \frac{ln\left(Z_{\rm t}\right) - \mu}{\sigma\sqrt{2}}\right)\right] + \frac{p_o}{\alpha-1}Z_{\rm t}^{-\alpha + 1}
\end{equation}
and
\begin{equation}
p_o = \frac{1}{\sigma Z_{\rm t} \sqrt{2 \pi}} {\rm exp}\left[-\frac{({\rm ln}(Z_{\rm t}) - \mu)^2}{2 \sigma^2} + \alpha {\rm ln}(Z_{\rm t}) \right]
\end{equation}.

We compute the numerical metal mass fraction PDFs for each metal species in our simulation using a fixed bin with of 0.05 dex. We fit $p(Z)$ to each of these using a Levenberg-Marquardt algorithm as implemented in \textsc{SciPy} \cite{SciPy}, stepping through possible values for $Z_{\rm t}$, set to the centers of each of these bins. The best of these fits is then compared to best fits using only a log-normal component or only a power-law component, and the best of these three is accepted. The log-normal + power-law PDF produces the best fit in nearly all cases.

@@

We argue here that the log-normal + power-law PDF can be a powerful tool for modelling the the metal fraction  PDFs of individual elements in galaxy models. The fits are not uniformly perfect but some deviation from a simple analytic model is expected in a complex, multi-phase ISM. In addition, some of this deviation, particularly in the WNM and WIM, could be caused by grouping together qualitatively distinct gas in a single phase; this would tend to broaden the distributions. Most importantly, however, the PDFs of the CNM, are indeed well fit by the adopted $p(Z)$. As this is the source of star forming gas in the ISM, the log-normal + power-law PDF appears useful to account for intrinsic scatter in stellar abundances in galaxy evolution models.

@@

For O, the median mass fraction is ordered by phase temperature. The HIM is significantly more enriched than the cooler phases by anywhere from 0.1 dex to 4 dex, fluctuating by $\pm$ 1 dex over the simulation time. The frequent large skew in the HIM (see second panel) and spread in the HIM (right two panels), coupled with its continual fluctuation, suggests that the HIM is not in equilibrium.
%This phase is poorly mixed because it is short lived, either cooling into different phases of the ISM or being ejected from the galaxy, and is continually enriched by new SN events.
Each cooler phase in O is progressively less enriched (lower median), with smaller skew and spread. The offset between phases and increasingly well mixed gas from hot to cold indicates that metal enrichment in the ISM of galaxies proceeds first through mixing on large scales in a hot phase, before progressively cooling through multiple phases until enriching star forming gas. This is the only explanation for how the cold gas can rapidly homogenize over the whole galaxy within $\sim$50 Myr, roughly when the cold phase exhibits a nearly constant spread (right panels). Individual enrichment events will have significantly higher metallicities than the ambient ISM in any phase, and will drive an increase in the difference between the mean and median of the PDF. These can be seen as the obvious spikes in the HIM and WIM. For O, the lack of these spikes in the two cold phases suggests again that enrichment does not occur directly in these phases, but proceeds more gradually through the warmer phases first.

@@

Although these trends are generally true for Ba, its evolution is much more complicated.
%In addition, the HIM is much less offset from the rest of the phases than is seen in O, with much less variability.
Unlike O, the spread and skew in Ba for the CNM, WNM, and WIM \textit{increase} in during the evolution, reaching differences in 90$^{\rm th}$ and 10$^{\rm th}$ percentiles of nearly 2 dex in the CNM and over 2 dex in the WNM and WIM. The HIM is seemingly unaffected by this trend, and simply fluctuates throughout the simulation. Given their lower energies, AGB winds more directly enrich the WNM and WIM, not the HIM as in supernovae. The consequence of this is clear in Figure~\ref{fig:log-normal} by the wider PDFs and longer power-law tails in Ba in these phases. These tails represent the most recently enriched gas, and is clearly much more locally confined than O.

%{\bf (move to discussion?)}:
The positive skew in all of the PDFs presented here implies that most of the mass of the galaxy has a metal fraction below what one would normally adopt as the average metallicity (i.e. the ratio between the total mass of metals and the total mass). Assuming star forming gas follows the same properties as the cold gas, this distinction is small ($\sim$ 0.2 dex), but significant, for elements released during SNe explosions, but can be very significant, up to $\sim$ 0.8 dex, for elements released in AGB winds. Chemical evolution models, especially one-zone models, follow the mean metal fraction, not median. These results indicate that these models are biased to overestimate gas and stellar elemental abundances.
. % However star formation may not be unbiased, and may preferentially come from gas sitting on the higher metal fraction tails.

To summarize, this figure demonstrates: 1) there are qualitative differences in how supernova injected elements (e.g. O, Mg) and AGB wind injected elements (e.g. N, Ba) are distributed through the ISM, with the latter having a broader range of variation and being less well mixed in all phases except the HIM, 2) hotter phases are more metal enriched, both because the cooler phases make up most of the initially unenriched mass of the ISM, and the hotter phases are more directly populated by recent enrichment events, 3) the cooler, denser phases, particularly for supernova injected elements, are more well mixed than the hot phases of the ISM, 4) the PDFs of metal mass fraction are best fit by a log-normal + power law function, and therefore 5) the median metallicity available for star formation rates lies below the mean galactic value. In the case of supernova injected elements, enrichment proceeds quickly through the HIM over the entire galaxy. For AGB injected elements, enrichment proceeds through the WIM and WNM, leading to longer mixing timescales and larger metal fraction variations in the ISM.

@@

\subsection{Physical Interpretation of the PDF}
\label{sec:interpretation}
Take the simple case of an initially primordial, uniform, isothermal medium of mass $M_o$ with initial metallicity $Z_{\rm o}$, containing a single, un-mixed enrichment event of mass $M_{\rm ej}$ whose size is small compared to the system and mass $M_{\rm ej} / M_o \ll 1$. Thus the background medium represents a virtually inexhaustible (but finite) source of un-enriched gas. In this case, $p(t,Z)$ initially takes the form of a double-delta function
\begin{equation}
p(t_{\rm o},Z) = \delta(Z_{\rm o}) + \frac{M_{\rm ej}}{M_o}\delta(Z - Z_{\rm ej}).
\end{equation}
If the enriched material mixes continually with the un-enriched gas at a constant rate, after some time this gas will have mixed with an equal amount of primordial gas \textbf{(lets take this time to be $\tau_{\rm mix}$). Therefore, we would have $p(\tau_{\rm mix},Z) = \delta(Z_{\rm o}) + \frac{2M_{\rm ej}}{M_o} \delta(Z - \frac{1}{2}Z_{\rm ej})$, $p(2\tau_{\rm mix},Z) = \delta(Z_{\rm o}) + \frac{4M_{\rm ej}}{M_o} \delta(Z - \frac{1}{4}Z_{\rm ej})$, and so on for other multiples of $\tau_{\rm mix}$.} This represents an inverse relationship between the mass of enriched gas and the metallicity of the enriched gas. \textbf{The superposition of the distributions of a single event evolving in time will appear as a power-law distribution with slope $\alpha = 1$.}

\textbf{Thus, if the gas is continually enriched by identical, well-separated enrichments events of mass $M_{\rm ej}$ and metallicity $Z_{\rm ej}$, the instantaneous $p(t,Z)$, or $p(Z)$, of these many events will be a power law in $Z$ with slope $\alpha = 1$, truncated at some minimim $Z$, related to the time since enrichment began, and some maximum, $Z_{\rm ej}$.}
% and thus a power-law evolution in time of the high metallicity portion of $p(Z)$ with slope $\alpha = 1$. 
The slope of the power-law, then, is determined by the rate of injection versus mixing with the ambient medium. A power-law index $\alpha < 1$ can occur when injection occurs more rapidly than the newly enriched gas can mix with the ambient medium. Steeper power-laws, $\alpha > 1$, develop when mixing occurs more rapidly than enrichment. If the ambient, primordial gas were truly infinite, the power-law would never completely encompass the delta function at $Z = Z_o$.

In reality, however, $M_o$ is not an inexhaustible reservoir of primordial gas. Eventually the entire ambient medium will become enriched to some $Z > Z_o$, and $p(Z)$ will consist entirely of a truncated power-law. As enrichment proceeds, gas near the low metallicity truncation of $p(Z)$, which still comprises much of the mass of the system, enriches towards higher metallicities in the power-law tail. This will produce a turnover at the low $Z$ limit of $p(Z)$. The low-turnover limit is produced by diffusion from many different sources, and is thus an additive process, which, as we noted above, tends to produce log-normal distributions. The physical interpretation of these two components is that the power-law tail represents newly enriched and poorly mixed gas that is above the average gas metallicity and is undergoing dilution, while the log-normal component represents the ambient medium that lies below the average gas metallicity and is undergoing enrichment.

>>>>

One-zone chemical evolution models assume homoegeneous mixing of metals from recent star formation into gas available for future star formation \citep[e.g.][]{Lanfranchi2006b,Kirby2011-III,Cote2017,Andrews2017}. While this assumes that metal mixing in the ISM plays no role in delaying future enrichment in star formation, accounting for this process is challenging. More complex models \citep[e.g.][]{SchonrichBinney2009,Pezzulli2016} employ multiple (usually radial) zones or follow multiple gas phases to attempt to account for these effects. How to properly account for multi-phase mixing, however, is still poorly understood. This is in large part because both these models and large-scale cosmological simulations lack the necessary fidelity to capture the detailed, multi-phase mixing process of metals in the ISM directly. 
%Consequently, following metal mixing, if treated in these models, requires assumptions about how metals mix within the ISM and how metals couple to galactic outflows. 
Recent hydrodynamics simulations have employed parameteric models to account for unresolved sub-grid metal mixing \citep{PanScannapiecoScalo2013,Sarmento2017}, which plays an important role in determining the chemical properties of galaxies \citep[e.g.][]{Shen2010, Pilkington2012, Few2012, Brook2014, FengKrumholz2014, Escala2018, Armillotta2018} 
% KVJ: citations to high-redshift work in this area
\textbf{and the enrichment process and chemical signatures of the first stars \citep[e.g.][]{Jeon2015,Ritter2015,Smith2015}.} Detailed hydrodynamics simulations incorporating a realistic multi-phase ISM and detailed stellar feedback are required to understand the details of metal mixing and metal outflows in galaxies.

@@

It is becoming increasingly valuable to develop a concrete theoretical understanding of galactic chemical evolution as a result of multiple, recent observational campaigns to probe detailed stellar abundances in our Milky Way and the Local Group, such as SEGUE \citep{Yanny2009}, RAVE \citep{Kunder2017}, APOGEE \citep{Anders2014}, and GALAH \citep{Buder2018}. Stellar abundances are directly imprinted with the enrichment pattern of their star forming cloud, whose chemical properties are determined by the process of turbulent metal mixing in the ISM. The degree to which we can associate "chemically tagged" stars as co-eval depends directly upon our understanding of metal enrichment and metal mixing in the ISM. Furthermore, this understanding is critical for using these observations to further deduce properties of a galaxy's evolutionary history. 
% KVJ asked to bring up this area of research and emphasize how it is lacking theoretical input
\textbf{One key aspect of this work has been a significant effort to characterize the number of independent dimensions accessible by the multi-dimensional chemical abundances observed in these studies \citep[e.g][]{Ting2012, Hogg2016,Jofre2017,Price-Jones2018}. Thus far, these studies have remained uninformed by hydrodynamics simulations and, conversely, these results cannot yet be used to constrain simulations. Doing so requires the kinds of high resolution, galaxy-scale multi-element chemodynamical simulations that have only become feasible in recent years.}

@@

%mm [this all seems to have been deleted in one version, but doesn't look like it should have been.  Down to ">>>>"] <<<<<<< HEAD
The top panel of Figure~\ref{fig:species_fractions} gives the mass fraction of each element at the end of the simulation (500~Myr) in each of four reservoirs: locked in stars (yellow), in the ISM (blue), outside the galaxy but within the virial radius (purple), and outside the virial radius (salmon), including gas that has left the domain. We subdivide the ISM by phase in the bottom panel, giving the mass fractions of each element in the cold neutral medium (CNM, $f_{\rm H_2} < 0.5$,  T$< 100$~K), warm neutral medium (WNM, $10^2~\rm{K}\le \rm{T} < 10^4~\rm{K}$), warm ionized medium (WIM, $10^4~\rm{K}\le \rm{T} < 10^{5.5}~\rm{K}$), the hot ionized medium (HIM T$\ge 10^{5.5}$~K), and locked in stars (yellow). 
%mm Again, with the exception of  H and He, we [H & He aren't metals]
    We
only consider metals produced self-consistently through our star formation and stellar feedback methods; the initial mass of each metal species is zero.

We find two major results.
%mm [reversed order of results to follow figure.  The opposite choice could also be made, by reversing the order of the figure...]
    First, 
only a small fraction of produced metals are retained within the dwarf galaxy, in agreement with observations of nearby dwarf galaxies \citep[see][]{Kirby2011-metals, McQuinn2015}; however, the retention factor varies 
%mm 
    among elements. The top panel shows a qualitative disagreement between the retention fractions of N and Ba (about 20\% for each) as compared to the rest of the metals ($\sim$ 4 -- 5\%). This suggests that individual metals \textit{do not} share the same dynamical evolution. 
%mm Clearly
       Thus, 
metal enrichment in galaxies is a phenomenon that cannot be fully captured using a single, global metallicity field. In this particular case, assuming that all metals behave the same would underestimate the N and Ba enrichment by a factor of up to five, at least for low mass dwarf galaxies.

    Second,
nearly all of the metals 
%mm
    retained in the disk
reside within neutral gas, mostly in the CNM; only a few percent
reside in the hot phases. The exact fraction varies with each species, most notably for carbon; these fluctuations are at most $\sim 10$\%. This is not surprising, as the cold phases represent the majority of the mass in the ISM, but, as shown in Section~\ref{sec:statistics}, even though the cold phases harbor most of the metals, the hot phases have significantly higher metal mass fractions.

@@

We find two major results. First, nearly all of the metals reside within neutral gas, mostly in the CNM; only a few percent reside in the hot phases. The exact fraction varies with each species, most notably for carbon; these fluctuations are at most $\sim 10$\%. This is not surprising, as the cold phases represent the majority of the mass in the ISM, but, as shown in Section~\ref{sec:statistics}, even though the cold phases harbor most of the metals, the hot phases have significantly higher metal mass fractions. Second, only a small fraction of produced metals are retained within the dwarf galaxy, in agreement with observations of nearby dwarf galaxies \citep[see][]{Kirby2011-metals, McQuinn2015}; however, the retention factor varies. The top panel shows a qualitative disagreement between the retention fractions of N and Ba (about 20\% for each) as compared to the rest of the metals ($\sim$ 4 -- 5\%). This suggests that individual metals \textit{do not} share the same dynamical evolution. Clearly, metal enrichment in galaxies is a phenomenon that cannot be fully captured using single, global metallicity field. In this particular case, assuming that all metals behave the same would underestimate the N and Ba enrichment by a factor of up to five, at least for low mass dwarf galaxies.
%mm [end of apparently deleted section] >>>>>>> 134a2fabac2aea2275cb3e8014308282b438742f

@@

%mm I think this material duplicates the first paragraph of the introduction.
% Chemical evolution models make varying approximations as to what fraction and on what timescales newly formed metals populate a galaxy's ISM and become available to enrich future generations of stars. In the simplest models, new metals are instantaneously available upon the formation of new stars, ignoring delays due to stellar lifetimes (\textit{refs, but maybe not if included in introduction}). Accounting for delays due to individual stellar lifetimes, loss from galactic winds, and dilution from accretion of pristine gas leads to models that can more accurately capture a variety of mean chemical properties of galaxies with some ability to account for spreads in abundances. In hydrodynamics simulations, there has been substantial work understanding how metals, often characterized as passive scalar fields, diffuse in both turbulent boxes and global galaxy models. 
%mm However, there is not  yet a complete model for how metals should mix and evolve in the complex, multi-phase ISM of real galaxies. To build towards this, we characterize the metal evolution and distributions in our galaxy below. 
      We characterize the metal distributions (in Sections~\ref{sec:log-normal} and \ref{sec:phase-pdfs}) and evolution (in Section~\ref{sec:statistics}) in our galaxy to build towards a  a complete model for how metals mix and evolve in the complex, multi-phase ISM of real galaxies.

%mm should most of this material be in the introduction, and just the last two sentences be here?
%   AE: I agree this is mostly redundant. I removed this
%Chemical evolution models make varying approximations as to what fraction and on what timescales newly formed metals populate a galaxy's ISM and become available to enrich future generations of stars. In the simplest models, new metals are instantaneously available upon the formation of new stars, ignoring delays due to stellar lifetimes (\textit{refs, but maybe not if included in introduction}). Accounting for delays due to individual stellar lifetimes, loss from galactic winds, and dilution from accretion of pristine gas leads to models that can more accurately capture a variety of mean chemical properties of galaxies with some ability to account for spreads in abundances. 
%In hydrodynamics simulations, there has been substantial work understanding how metals, often characterized as passive scalar fields, diffuse in both turbulent boxes and global galaxy models. However, there is not  yet a complete model for how metals should mix and evolve in the complex, multi-phase ISM of real galaxies. To build towards this, we characterize the metal evolution and distributions in our galaxy below.

@@

The log-normal distribution is found often in nature, generally describing 
%mm
    multiplicative
processes with non-negative values that grow with time. In astrophysics, for example, the log-normal distribution can be used to describe the time evolution of the star formation rate density \citep[see ][]{Gladders2013,Abramson2016,Diemer2017}. In addition, as expected from analytic theory \citep{Vazquez-Semadeni1994}, isothermal turbulence gives rise to log-normal density probability distribution functions \citep[PDFs;][]{Padoan1997, Passot1998, Ostriker1999,PadoanNordlund2002,KrumholzMcKee2005,Federrath2008}. Although these PDFs are only log-normal in simulations containing a more realistic, multi-phase ISM \citep{Scalo1998} if the disk is very stable \citep{WadaNorman2007}, individual phases within the ISM do exhibit some log-normality \citep{Tasker2009, Tasker2011,Joung2009,PriceFederrathBrunt2011, HopkinsQuataertMurray2012}. It has been shown that the 3D density PDF and the column density PDF, in both simulations and observations, have a characteristic shape. This includes a log-normal component, generated by multiplicative processes---in this case shocks and the turbulent cascade in the ISM---and a power-law component at high densities arising from the additive combination of individual, self-gravitating cloud structures \citep{Vazquez-Semadeni1994,Burkhart2009, FederrathKlessen2013, Collins2012, Myers2015, Burkhart2017, Chen2017}.

@@

We follow \citet{Collins2012}, \citet{Burkhart2017}, and \citet{Chen2017} in constructing our piecewise PDF. We define the distribution of metals in the ISM as a function of the fraction of mass contained at a given metallicity, $Z$, or metal mass fraction, $Z_i$, where $i$ denotes an individual element. This PDF is given as
\begin{align*}
  p(Z) =
  \begin{cases}
    \frac{N}{\sigma Z \sqrt{2\pi}} \rm{exp}\left[-\frac{(\rm{ln}(Z) - \mu)^2}{2\sigma^2}\right],
    & Z < Z_{\rm{t}} \\
    % \multicolumn{1}{@{}c@{\quad}}{1} % variant with \multicolumn
    N p_o Z^{-\alpha},
    & Z > Z_{\rm{t}}
\end{cases}
\end{align*}
where $N$ is a normalization constant, $p_o$ ensures continuity between the two components, $\mu$ and $\sigma$ are the log-mean and width of the log-normal component, $\alpha$ is the power-law slope,  and Z$_{\rm t}$ is the metal fraction at the transition between the log-normal and power-law components. When fitting this PDF, we only enforce continuity and $\int_0^{\infty} p(Z) dZ = 1$, leaving $\alpha$, $\mu$, $\sigma$, and $Z_{\rm t}$ as free parameters. These conditions set $N$ and $p_o$ to
\begin{equation}
N = \frac{1}{2} \left[ 1 + \rm{erf}\left( \frac{ln\left(Z_{\rm t}\right) - \mu}{\sigma\sqrt{2}}\right)\right] + \frac{p_o}{\alpha-1}Z_{\rm t}^{-\alpha + 1}
\end{equation}
and
\begin{equation}
p_o = \frac{1}{\sigma Z_{\rm t} \sqrt{2 \pi}} {\rm exp}\left[-\frac{({\rm ln}(Z_{\rm t}) - \mu)^2}{2 \sigma^2} + \alpha {\rm ln}(Z_{\rm t}) \right]
\end{equation}.

We compute the numerical metal mass fraction PDFs for each metal species in our simulation using a fixed bin 
%mm with 
         width
of 0.05 dex. We fit $p(Z)$ to each of these using a Levenberg-Marquardt algorithm as implemented in \textsc{SciPy} \cite{SciPy}, stepping through possible values for $Z_{\rm t}$, set to the centers of each of these bins. The best of these fits is then compared to best fits using only a log-normal component or only a power-law component, and the best of these three is accepted. The log-normal + power-law PDF produces the best fit in nearly all cases.

@@

We argue here that the log-normal + power-law PDF can be a powerful tool for modelling the metal fraction  PDFs of individual elements in galaxy models. The fits are not uniformly perfect but some deviation from a simple analytic model is expected in a complex, multi-phase ISM. In addition, some of this deviation, particularly in the WNM and WIM, could be caused by grouping together qualitatively distinct gas in a single phase; this would tend to broaden the distributions. Most importantly, however, the PDFs of the CNM, are indeed well fit by the adopted $p(Z)$. As this is the source of star forming gas in the ISM, the log-normal + power-law PDF appears useful to account for intrinsic scatter in stellar abundances in galaxy evolution models.

@@

For O, the median mass fraction is ordered by phase temperature. The HIM is significantly more enriched than the cooler phases by anywhere from 0.1 dex to 4 dex, fluctuating by $\pm 1$ dex over the simulation time. The frequent large skew in the HIM (see second panel) and spread in the HIM (right two panels), coupled with its continual fluctuation, suggests that the HIM is not in equilibrium.
%This phase is poorly mixed because it is short lived, either cooling into different phases of the ISM or being ejected from the galaxy, and is continually enriched by new SN events.
Each cooler phase in O is progressively less enriched (lower median), with smaller skew and spread. The offset between phases and increasingly well mixed gas from hot to cold indicates that metal enrichment in the ISM of galaxies proceeds first through mixing on large scales in a hot phase, before progressively cooling through multiple phases until enriching star forming gas. This 
%mm is the only explanation for [that's perhaps too strong a claim]
    can explain
how the cold gas can rapidly homogenize over the whole galaxy within $\sim$50 Myr, roughly when the cold phase exhibits a nearly constant spread (right panels). Individual enrichment events 
%mm will 
have significantly higher metallicities than the ambient ISM in any phase, and 
%mm will 
drive an increase in the difference between the mean and median of the PDF. These can be seen as the obvious spikes in the HIM and WIM. For O, the lack of these spikes in the two cold phases suggests again that enrichment does not occur directly in these phases, but proceeds more gradually through the warmer phases first.

@@

Although these trends are generally true for Ba, its evolution is much more complicated.
%In addition, the HIM is much less offset from the rest of the phases than is seen in O, with much less variability.
Unlike O, the spread and skew in Ba for the CNM, WNM, and WIM \textit{increase} in during the evolution, reaching differences in 90$^{\rm th}$ and 10$^{\rm th}$ percentiles of nearly 2 dex in the CNM and over 2 dex in the WNM and WIM. The HIM is seemingly unaffected by this trend, and simply fluctuates throughout the simulation. Given their lower energies, AGB winds more directly enrich the WNM and WIM, not the HIM as in supernovae. The consequence of this is clear in Figure~\ref{fig:log-normal} by the wider PDFs and longer power-law tails in Ba in these phases. These tails represent the most recently enriched gas, 
%mm and 
        which
is clearly much more locally confined than O.

%{\bf (move to discussion?)}:
The positive skew in all of the PDFs presented here implies that most of the mass of the galaxy has a metal fraction below what one would normally adopt as the average metallicity (i.e.\ the ratio between the total mass of metals and the total mass). Assuming star forming gas follows the same properties as the cold gas, this distinction is small ($\sim$ 0.2 dex), 
%mm but
   though 
significant, for elements released during SNe explosions, but can be very significant, up to $\sim$ 0.8 dex, for elements released in AGB winds. Chemical evolution models, especially one-zone models, follow the mean metal fraction, rather than the median. 
%mm These results indicate that these 
            Our results indicate that such
models are biased to overestimate gas and stellar elemental abundances.
. % However star formation may not be unbiased, and may preferentially come from gas sitting on the higher metal fraction tails.

To summarize, Figure~\ref{fig:phase-statistics} demonstrates: 1) there are qualitative differences in how supernova injected elements (e.g. O, Mg) and AGB wind injected elements (e.g. N, Ba) are distributed through the ISM, with the latter having a broader range of variation and being less well mixed in all phases except the HIM; 2) hotter phases are more metal enriched, both because the cooler phases make up most of the initially unenriched mass of the ISM and because the hotter phases are more directly populated by recent enrichment events; 3) the cooler, denser phases, particularly for supernova injected elements, are more well mixed than the hot phases of the ISM; 4) the PDFs of metal mass fraction are best fit by a log-normal + power law function; and therefore 5) the median metallicity available for star formation 
%mm rates 
lies below the mean galactic value. In the case of supernova injected elements, enrichment proceeds quickly through the HIM over the entire galaxy. For AGB injected elements, enrichment proceeds through the WIM and WNM, leading to longer mixing timescales and larger metal fraction variations in the ISM.

@@

\subsection{Physical Interpretation of the PDF}
\label{sec:interpretation}
%
% KVJ wanted clarification on this argument. I believe my added text 
% does this sufficiently.
Take the simple case of an initially primordial, uniform, isothermal medium of mass $M_o$ with initial metallicity $Z_{\rm o}$, containing a single, un-mixed enrichment event of mass $M_{\rm ej}$ whose size is small compared to the system and mass $M_{\rm ej} / M_o \ll 1$. Thus the background medium represents a virtually inexhaustible (but finite) source of un-enriched gas. In this case, $p(t,Z)$ initially takes the form of a double-delta function
\begin{equation}

p(t_{\rm o},Z) = \delta(Z_{\rm o}) + \frac{M_{\rm ej}}{M_o}\delta(Z - Z_{\rm ej}).
\end{equation}
%mm [edited the rest of this paragraph, and the next though I don't think there are any substantive changes unmarked.]
If the enriched material mixes continually with the un-enriched gas at a constant rate, after some time  $\tau_{\rm mix}$ this gas will have mixed with an equal amount of primordial gas. \textbf{At this time, $p(\tau_{\rm mix},Z) = \delta(Z_{\rm o}) + (2M_{\rm ej}/M_o) \delta(Z - (1/2)Z_{\rm ej})$, $p(2\tau_{\rm mix},Z) = \delta(Z_{\rm o}) + (4M_{\rm ej}/M_o)\delta(Z - (1/4) Z_{\rm ej})$, and so on for other multiples of $\tau_{\rm mix}$.} This represents an inverse relationship between the mass of enriched gas and the metallicity of the enriched gas. \textbf{The superposition of the distributions of a single event evolving in time will appear as a power-law distribution with slope $\alpha = 1$.}

\textbf{Thus, if the gas is continually enriched by identical, well-separated enrichment events of mass $M_{\rm ej}$ and metallicity $Z_{\rm ej}$, the instantaneous distribution $p(t,Z)$
%mm , or $p(Z)$, 
of these many events will be a power law in $Z$ with slope $\alpha = 1$, truncated at some minimim $Z$ (related to the time since enrichment began) and some maximum, $Z_{\rm ej}$.}
% and thus a power-law evolution in time of the high metallicity portion of $p(Z)$ with slope $\alpha = 1$. 
The slope of the power-law, then, is determined by the rate of injection versus mixing with the ambient medium. A power-law index $\alpha < 1$ can occur when injection occurs more rapidly than the newly enriched gas can mix with the ambient medium. Steeper power-laws, $\alpha > 1$, develop when mixing occurs more rapidly than 
%mm enrichment. 
         injection.
If the ambient, primordial gas were truly infinite, the power-law would never completely encompass the delta function at $Z = Z_o$.
